A southern hemisphere flux scale for 21cm epoch of reionization experiments

### 2013-04-22 ms.tex
Just rewrap of text (no edits).

Neutral hydrogen is visible during reionization as $\sim$30mK excess surface brightness over the CMB punctuated both spectrally and spatially by regions of zero emission.
This patchy signal is predicted to be visible everywhere on the sky at size scales up to degrees, or about $0.1$cMpc$^{-1}$.   To increase the surface brightness sensitivity without building costly dishes, MWA, PAPER and LOFAR have chosen to use combinations of phased and/or correlated dipoles. By design also cover much wider fields of view ($>10$\arcdeg) and bandwidths ($\sim 100$\% fractional) than traditional dish telescopes.   As the elements can not be physically pointed, the apparent flux scale varies across the sky. This direction dependent gain is currently uncertain to 20\% or higher \citep{Jacobs:2013p9713}.  The ideal solution is to use a wide-grid of well-known calibrators to map the primary beam and set the flux scale.  
%The position dependent gain varies for each instrument.   LOFAR and MWA have a range of electrically steerable beams each with a different shape. For MWA and LOFAR, the number of high quality calibration sources is more important.  PAPER has a single broad, 45\arcdeg wide, primary beam; sources at nearby declinations sample the same primary beam many times.
% This will in turn provide a wide base to assess the accuracy of the primary calibrator which sets the overall amplitude of the EoR power spectrum.

@@

 \section{Observations and Data Reduction}
 \label{sec:Observations}
 Measurements are derived from observations using  the east-west dipole arms of 64 PAPER antennas 
deployed in the Karoo Radio Observatory site in South Africa (see Figure \ref{fig:antpos}).  
A 100-MHz band from 100-200MHz was
correlated with 2048 frequency channels and integrated for 10.7 seconds before visibilities were stored.
Observations included here on  July 4, 2011, running
from JD2455748.17 to JD2455748.72. and October 17, 2011 running from JD2455852.2 to JD2455852.6.
In both seasons two antennas were omitted owing to malfunctioning signal path. This 20 hour long combined dataset provides observations provides complete hour angle coverage for the entire 24 hours of Right Ascension. The July portion of the dataset comes from the same observing campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}. 
%July (\#40,\#55), September (\#7,\#28)

%COMPRESSION
\textbf{Compression}\\
In pre-processing, we use delay/delay-rate (DDR) filters \citep{Parsons:2009p7859} to identify
radio-frequency interference (RFI) events, and as part of a data compression
technique that reduces data volume by over a factor of 40.  A more detailed description may be found in Appendix A of \cite{Parsons2013b}, which uses the same compression method on PAPER power spectrum observations. Here we summarize the process.

@@

%CALIBRATION
\textbf{Antenna calibration}\\
Antennae delays and amplitudes were found by fitting a point source visibility model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly modeled by a single point-source, but the solution differences are minimized by averaging over the three independent solutions. These same calibration solutions have also been successfully applied in the power spectrum analysis by Pober (2013) and Centaurus A imaging by Stefan (2013).

@@

\textbf{Beamforming}\\
Spectral time-series are computed by beam-forming to the selected sky locations. A beam is formed by phasing baselines to the desired location and summing over baselines.  %Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.   By using both seasons of data we were able to match all measurements with calibrator measurements, making this cut moot. 
 These complex spectra are then delay-delay rate filtered to remove spectrally smooth sources far from phase center \citep{Parsons:2009p7859} (cf the LOFAR de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent spectrum. This is then averaged in time,  weighting by a model of the primary beam. This down-weighting, or multiplying by the primary beam, should be clearly distinguished from up-weighting, which we are at pains to avoid.  Weighting by another factor of the primary beam is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800} and reduces the contribution of noisy low elevation measurements.  The result is equivalent to a very long earth rotation synthesis image with a single image pixel. When combined with the filtering it is a robust and simple method for measuring spectra of unresolved sources. 
\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/PicA_Oct2011_uv_coverage.png}
\caption{The effective uv coverage, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session. \label{fig:uv_coverage}}
\end{figure}

The beam-forming method assumes the target is a point source. Our primary target, Pictor A, is slightly resolved by PAPER, and merits closer attention. Pictor A is a double-lobed radio galaxy with a main lobe separation of 7\arcmin. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by PAPER's 15\arcmin synthesized beam. However, given the high SNR of the observations, resolution effects are observers, in a slight decrease in flux on the longest ($\sim$300m) baselines. We account for this by weighting baselines in the beam form step according to a model of structure observed by \citet{Perley:1997p9312} at 330MHz, which they found to be consistent with their more limited 74MHz images as well as the detailed high frequency maps.  The normalized image is Fourier transformed and sampled at the desired uv spacing by spline interpolation. These samples are used to weight each baseline contribution in the baseline sum. The result is an estimate of the total integrated flux for Pictor A. Where the resolution is highest, at the top of the band, the correction is 3\%. At the bottom of the band, where the resolution size has grown to 19\arcmin, the correction is only 0.6\%. The resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.
\begin{figure}
\includegraphics[width=0.96\textwidth]{plots/picA_Perley.png}
\caption{Pictor A imaged at 330MHz by the VLA \citep{Perley:1997p9312}. Black circle indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.  To correct for the small residual structure in the PAPER measurements we interpolated the PAPER baselines in the uv plane. At the highest frequency this led to a 3\% correction, at the lowest frequency, 0.6\%.  \label{fig:pic_perley}}
\end{figure}

%BANDPASS CALIBRATION
\textbf{Spectral calibration}\\
\label{sec:Calibration}
The gain of each channel is the product of an overall instrumental passband and the spectral dependence of the primary beam in the direction of the source.  Sources sharing the same track through the primary beam will have the same average spectral gain function resulting from frequency dependent primary beam attenuation.   We matched each measured source spectrum time sample to the nearest sample (in altitude/azimuth) of a calibrator source (J2331-416)\footnote{This source was chosen for the amount of data found in the literature and the apparent smoothness of the spectrum.}.  We then, average the two matched data streams in time.  Since both tracks make the same slice through the primary beam, they will have the same average effective gain. Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a bandpass gain.  After calibrating the raw 203 channel spectra with this bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing the standard deviation as an estimate of the error.

\textbf{Catalogs}\\
Data for prior comparison was pulled from two major sources. Catalog values for Pictor A, and the flux calibration sources were pulled directly from the NASA/IPAC Extragalactic Database (NED) \footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources between bands is made difficult by changes in resolution, spectral curvature, and resolved multi-scale structure.  For a small number of sources these problems can be ameliorated by inspection of the spectra, source names, coordinates,  and originating publications. However for a large sample of sources this becomes unwieldily and prone to error. Thus for the larger number of samples we make use of the Vollmer et al meta-catalog which takes pains to match multi-wavelength observations \citep{Vollmer:2010p6422}.% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.

\textbf{Flux Scale}\\
\label{sec:flux_scale}
At this stage each source flux is tied to a model fit on the catalog values of J2331-416. The accuracy of this fit and the implied uncertainty in the flux scale limits the accuracy of the PAPER measurements..  To refine the flux scale, we bootstrap a single global flux scale correction factor using 5 sources selected for their brightness, spectral linearity and data availability\footnote{Calibration sources: 2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete spectral model we go beyond the data found in SPECFIND, using all spectral measurements below 2GHz found in the NED database.  These catalog measurements are primarily by Parkes, and Molonglo with the best precision coming from the Wills fluxes at 538 and 634 MHz (when available). Where error bars are not given, we assume uncertainty of 25\%.

@@

 \section{Spectral Results}
 \label{sec:fits}
The primary purpose of this observation is to produce a high quality Pictor A spectrum. As a verification measure we have observed many other sources at the same declination for comparison against previous observations.  Our comparison metric will be the degree to which the PAPER data are consistent with previous observations,given a model and, if consistent, they improve on the precision of our spectral model parameters.

@@

%0008-421#
%1243-412#
%1247-401#
%1315-460
%TODO round up the source counts
In the 59 sources measured, four demonstrated poor convergence fitting a single spectral index to both the PAPER data and prior catalog data. In three cases\footnote{1243-412,1247-401,1315-460} %TODO update
these sources are in the Centaurus A/galactic plane region. Though the beam forming method provides relatively high dynamic range of $\sim$100:1 it is unable to distinguish between these sources and the bright diffuse Centaurus and galactic structure. The last source, 0008-421, was not detected by previous PAPER observations and exhibits flattening at higher frequencies, most likely due to synchrotron self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains arrived at a stable posterior distribution. The spectral index parameters for these chains are given in table \ref{tab:fits}.

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_2140-434_0007-446_0704-427_gain_mcmc_chain_gain_conf.png}

\caption{The marginalized PAPER flux scale factor posterior probability distribution function bootstrapped from the NED database listings for 2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.  \label{fig:gain}}
\end{figure*}

\begin{figure*}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pictor_spectrum.png}
\includegraphics[width=0.49\textwidth]{plots/pic_SI_MCMC.png}
\caption{Using new PAPER results to constrain the spectrum of Pictor A.
On the left, the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey cloud). Inset allows comparison between the 10MHz averaged points with the 403kHz points (grey). The oscillations in the PAPER spectrum are residual side lobe contamination from other sources and are well represented by the error bars.  The most reliable prior measurements (dots) are those by \cite{Wills:1975p9314} at 580MHz and 635MHz \citep{Perley:1997p9312}. The rest are from with Culgoora \cite{Slee:1995p7541} or Parkes  \cite{Otrupcek:1991p8780} and have been set to the (extrapolated) \citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC fits are shown in blue. On the right, the grey contour indicates the 76\% confidence interval for 150MHz flux and spectral index given the prior data. Black folds in the PAPER data. }
\label{fig:pic_spectrum}
\end{figure*}

@@

\section*{Acknowledgements}
The PAPER project is supported by the National Science Foundation (awards 0804508, 1129258, and 1125558), and a generous grant from the Mt. Cuba Astronomical Association.

@@

\section*{Appendix: Model Fitting}
In this paper we estimate spectral model parameters and flux calibration in a Bayesian way by calculating and marginalizing the posterior probability of the data, past and present, given a spectral and instrumental model.   This method offers improved repeatability by specifying a single objective function that represents the quality of the model fit and naturally defines the errors on the parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or \citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent astrophysical example by \cite{Press:1997p9783}.

@@

\begin{figure}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
\caption{A more detailed view of the posterior probability distribution. On the left Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8. Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.  As above, grey for  the fit to catalog data, black for joint catalog and PAPER fit. }
\end{figure}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_1.png}
\end{center}
\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs1}. Sources used to bootstrap the flux calibration are noted with a *.}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_2.png}
\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs2} Sources used to bootstrap the flux calibration are noted with a *.}
\end{center}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_3.png}
\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs3} Sources used to bootstrap the flux calibration are noted with a *.}
\end{center}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{center}
%zero overlap
\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1320-446_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1459-417_SI_MCMC.png} %0
\includegraphics[width=2in]{plots/cen_SI_MCMC.png} %0.0
\end{center}
\caption{These sources offer results at odds with previous measurements. These have small enough error bars to require a deviation from spectral index fit suggested by prior catalog measurements. All are near Centaurus A (see Figure \ref{fig:error_map}), a very bright, extended source, and are likely evidence for side lobe contamination.  Side lobes from distant sources manifest as ripples in the spectrum, increasing the error bars (e.g. the sources listed in Figure \ref{fig:SI_contour_bad}). However, the sources shown here are close enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz and does not fall into the rms, but rather into the mean. Thus these few points have anomalously high fluxes and small error bars. }
\label{fig:SI_contour_new}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.png}
\caption{A map of the radio sky centered on the south pole \citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size scaled by agreement with prior data (inverse ``improvement index", see \S\ref{sec:fits}). Black dots indicate sources with $\le0$ improvement score. For these the fit quality decreases with addition of PAPER data or the model revision disagrees completely with the prior estimate due to side lobes or spectral curvature.  We estimate that   \label{fig:error_map}}
\end{figure*}

>>>>

Neutral hydrogen is visible during reionization as $\sim$30mK excess surface
brightness over the CMB punctuated both spectrally and spatially by regions of
zero emission.  This patchy signal is predicted to be visible everywhere on the
sky at size scales up to degrees, or about $0.1$cMpc$^{-1}$.   To increase the
surface brightness sensitivity without building costly dishes, MWA, PAPER and
LOFAR have chosen to use combinations of phased and/or correlated dipoles. By
design also cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.   As the elements
can not be physically pointed, the apparent flux scale varies across the sky.
This direction dependent gain is currently uncertain to 20\% or higher
\citep{Jacobs:2013p9713}.  The ideal solution is to use a wide-grid of
well-known calibrators to map the primary beam and set the flux scale.

%The position dependent gain varies for each instrument.   LOFAR and MWA have a range of electrically steerable beams each with a different shape. For MWA and LOFAR, the number of high quality calibration sources is more important.  PAPER has a single broad, 45\arcdeg wide, primary beam; sources at nearby declinations sample the same primary beam many times.
% This will in turn provide a wide base to assess the accuracy of the primary calibrator which sets the overall amplitude of the EoR power spectrum.

@@

 \section{Observations and Data Reduction}
 \label{sec:Observations}

 Measurements are derived from observations using  the east-west dipole arms of
64 PAPER antennas deployed in the Karoo Radio Observatory site in South Africa
(see Figure \ref{fig:antpos}).  A 100-MHz band from 100-200MHz was correlated
with 2048 frequency channels and integrated for 10.7 seconds before
visibilities were stored.  Observations included here on  July 4, 2011, running
from JD2455748.17 to JD2455748.72. and October 17, 2011 running from
JD2455852.2 to JD2455852.6.  In both seasons two antennas were omitted owing to
malfunctioning signal path. This 20 hour long combined dataset provides
observations provides complete hour angle coverage for the entire 24 hours of
Right Ascension. The July portion of the dataset comes from the same observing
campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}. 
%July (\#40,\#55), September (\#7,\#28)

%COMPRESSION
\textbf{Compression}\\

In pre-processing, we use delay/delay-rate (DDR) filters
\citep{Parsons:2009p7859} to identify radio-frequency interference (RFI)
events, and as part of a data compression technique that reduces data volume by
over a factor of 40.  A more detailed description may be found in Appendix A of
\cite{Parsons2013b}, which uses the same compression method on PAPER power
spectrum observations. Here we summarize the process.

@@

%CALIBRATION
\textbf{Antenna calibration}\\

Antennae delays and amplitudes were found by fitting a point source visibility
model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
modeled by a single point-source, but the solution differences are minimized by
averaging over the three independent solutions. These same calibration
solutions have also been successfully applied in the power spectrum analysis by
Pober (2013) and Centaurus A imaging by Stefan (2013).

@@

\textbf{Beamforming}\\

Spectral time-series are computed by beam-forming to the selected sky
locations. A beam is formed by phasing baselines to the desired location and
summing over baselines.  
%Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.   By using both seasons of data we were able to match all measurements with calibrator measurements, making this cut moot.

 These complex spectra are then delay-delay rate filtered to remove spectrally
smooth sources far from phase center \citep{Parsons:2009p7859} (cf the LOFAR
de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent
spectrum. This is then averaged in time,  weighting by a model of the primary
beam. This down-weighting, or multiplying by the primary beam, should be
clearly distinguished from up-weighting, which we are at pains to avoid.
Weighting by another factor of the primary beam is an effective approximation
of inverse-variance weighting \citep{Pober:2012p8800} and reduces the
contribution of noisy low elevation measurements.  The result is equivalent to
a very long earth rotation synthesis image with a single image pixel. When
combined with the filtering it is a robust and simple method for measuring
spectra of unresolved sources.

\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/PicA_Oct2011_uv_coverage.png}
\caption{The effective uv coverage, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session. \label{fig:uv_coverage}}
\end{figure}

The beam-forming method assumes the target is a point source. Our primary
target, Pictor A, is slightly resolved by PAPER, and merits closer attention.
Pictor A is a double-lobed radio galaxy with a main lobe separation of
7\arcmin. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by
PAPER's 15\arcmin synthesized beam. However, given the high SNR of the
observations, resolution effects are observers, in a slight decrease in flux on
the longest ($\sim$300m) baselines. We account for this by weighting baselines
in the beam form step according to a model of structure observed by
\citet{Perley:1997p9312} at 330MHz, which they found to be consistent with
their more limited 74MHz images as well as the detailed high frequency maps.
The normalized image is Fourier transformed and sampled at the desired uv
spacing by spline interpolation. These samples are used to weight each baseline
contribution in the baseline sum. The result is an estimate of the total
integrated flux for Pictor A. Where the resolution is highest, at the top of
the band, the correction is 3\%. At the bottom of the band, where the
resolution size has grown to 19\arcmin, the correction is only 0.6\%. The
resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.

\begin{figure}
\includegraphics[width=0.96\textwidth]{plots/picA_Perley.png}
\caption{
Pictor A imaged at 330MHz by the VLA \citep{Perley:1997p9312}. Black circle
indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.  To
correct for the small residual structure in the PAPER measurements we
interpolated the PAPER baselines in the uv plane. At the highest frequency this
led to a 3\% correction, at the lowest frequency, 0.6\%.
\label{fig:pic_perley}}
\end{figure}

%BANDPASS CALIBRATION
\textbf{Spectral calibration}\\
\label{sec:Calibration}

The gain of each channel is the product of an overall instrumental passband and
the spectral dependence of the primary beam in the direction of the source.
Sources sharing the same track through the primary beam will have the same
average spectral gain function resulting from frequency dependent primary beam
attenuation.   We matched each measured source spectrum time sample to the
nearest sample (in altitude/azimuth) of a calibrator source
(J2331-416)\footnote{This source was chosen for the amount of data found in the
literature and the apparent smoothness of the spectrum.}.  We then, average the
two matched data streams in time.  Since both tracks make the same slice
through the primary beam, they will have the same average effective gain.
Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
bandpass gain.  After calibrating the raw 203 channel spectra with this
bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
the standard deviation as an estimate of the error.

\textbf{Catalogs}\\

Data for prior comparison was pulled from two major sources. Catalog values for
Pictor A, and the flux calibration sources were pulled directly from the
NASA/IPAC Extragalactic Database (NED)
\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
between bands is made difficult by changes in resolution, spectral curvature,
and resolved multi-scale structure.  For a small number of sources these
problems can be ameliorated by inspection of the spectra, source names,
coordinates,  and originating publications. However for a large sample of
sources this becomes unwieldily and prone to error. Thus for the larger number
of samples we make use of the Vollmer et al meta-catalog which takes pains to
match multi-wavelength observations \citep{Vollmer:2010p6422}.
% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.

\textbf{Flux Scale}\\
\label{sec:flux_scale}

At this stage each source flux is tied to a model fit on the catalog values of
J2331-416. The accuracy of this fit and the implied uncertainty in the flux
scale limits the accuracy of the PAPER measurements..  To refine the flux
scale, we bootstrap a single global flux scale correction factor using 5
sources selected for their brightness, spectral linearity and data
availability\footnote{Calibration sources:
2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
spectral model we go beyond the data found in SPECFIND, using all spectral
measurements below 2GHz found in the NED database.  These catalog measurements
are primarily by Parkes, and Molonglo with the best precision coming from the
Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
given, we assume uncertainty of 25\%.

@@

 \section{Spectral Results}
 \label{sec:fits}

The primary purpose of this observation is to produce a high quality Pictor A
spectrum. As a verification measure we have observed many other sources at the
same declination for comparison against previous observations.  Our comparison
metric will be the degree to which the PAPER data are consistent with previous
observations,given a model and, if consistent, they improve on the precision of
our spectral model parameters.

@@

%0008-421#
%1243-412#
%1247-401#
%1315-460
%TODO round up the source counts

In the 59 sources measured, four demonstrated poor convergence fitting a single
spectral index to both the PAPER data and prior catalog data. In three
cases\footnote{1243-412,1247-401,1315-460} %TODO update these sources are in
the Centaurus A/galactic plane region. Though the beam forming method provides
relatively high dynamic range of $\sim$100:1 it is unable to distinguish
between these sources and the bright diffuse Centaurus and galactic structure.
The last source, 0008-421, was not detected by previous PAPER observations and
exhibits flattening at higher frequencies, most likely due to synchrotron
self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains
arrived at a stable posterior distribution. The spectral index parameters for
these chains are given in table \ref{tab:fits}.

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_2140-434_0007-446_0704-427_gain_mcmc_chain_gain_conf.png}
\caption{
The marginalized PAPER flux scale factor posterior probability distribution
function bootstrapped from the NED database listings for
2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.
\label{fig:gain}}
\end{figure*}

\begin{figure*}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pictor_spectrum.png}
\includegraphics[width=0.49\textwidth]{plots/pic_SI_MCMC.png}
\caption{
Using new PAPER results to constrain the spectrum of Pictor A.  On the left,
the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey
cloud). Inset allows comparison between the 10MHz averaged points with the
403kHz points (grey). The oscillations in the PAPER spectrum are residual side
lobe contamination from other sources and are well represented by the error
bars.  The most reliable prior measurements (dots) are those by
\cite{Wills:1975p9314} at 580MHz and 635MHz \citep{Perley:1997p9312}. The rest
are from with Culgoora \cite{Slee:1995p7541} or Parkes
\cite{Otrupcek:1991p8780} and have been set to the (extrapolated)
\citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC
fits are shown in blue. On the right, the grey contour indicates the 76\%
confidence interval for 150MHz flux and spectral index given the prior data.
Black folds in the PAPER data.
} \label{fig:pic_spectrum}
\end{figure*}

@@

\section*{Acknowledgements}

The PAPER project is supported by the National Science Foundation (awards
0804508, 1129258, and 1125558), and a generous grant from the Mt. Cuba
Astronomical Association.

@@

\section*{Appendix: Model Fitting}

In this paper we estimate spectral model parameters and flux calibration in a
Bayesian way by calculating and marginalizing the posterior probability of the
data, past and present, given a spectral and instrumental model.   This method
offers improved repeatability by specifying a single objective function that
represents the quality of the model fit and naturally defines the errors on the
parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or
\citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent
astrophysical example by \cite{Press:1997p9783}.

@@

\begin{figure}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
\caption{
A more detailed view of the posterior probability distribution. On the left
Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8.
Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.
As above, grey for  the fit to catalog data, black for joint catalog and PAPER
fit.
}
\end{figure}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_1.png}
\end{center}
\caption{
PAPER spectra of 16 sources compared against existing data out of
\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
Figure \ref{fig:pic_spectrum}.\label{fig:srcs1}. Sources used to bootstrap the
flux calibration are noted with a *.
}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_2.png}
\caption{
PAPER spectra of 16 sources compared against existing data out of
\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
Figure \ref{fig:pic_spectrum}.\label{fig:srcs2} Sources used to bootstrap the
flux calibration are noted with a *.
}
\end{center}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_3.png}
\caption{
PAPER spectra of 16 sources compared against existing data out of
\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
Figure \ref{fig:pic_spectrum}.\label{fig:srcs3} Sources used to bootstrap the
flux calibration are noted with a *.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{center}
%zero overlap
\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1320-446_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1459-417_SI_MCMC.png} %0
\includegraphics[width=2in]{plots/cen_SI_MCMC.png} %0.0
\end{center}
\caption{
These sources offer results at odds with previous measurements. These have
small enough error bars to require a deviation from spectral index fit
suggested by prior catalog measurements. All are near Centaurus A (see Figure
\ref{fig:error_map}), a very bright, extended source, and are likely evidence
for side lobe contamination.  Side lobes from distant sources manifest as
ripples in the spectrum, increasing the error bars (e.g. the sources listed in
Figure \ref{fig:SI_contour_bad}). However, the sources shown here are close
enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz
and does not fall into the rms, but rather into the mean. Thus these few points
have anomalously high fluxes and small error bars. 
} \label{fig:SI_contour_new}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.png}
\caption{
A map of the radio sky centered on the south pole
\citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size
scaled by agreement with prior data (inverse ``improvement index", see
\S\ref{sec:fits}). Black dots indicate sources with $\le0$ improvement score.
For these the fit quality decreases with addition of PAPER data or the model
revision disagrees completely with the prior estimate due to side lobes or
spectral curvature.  We estimate that   \label{fig:error_map}
}
\end{figure*}
